Tree size, microhabitat, and hydraulic traits (interactively) shape drought response in a temperate broadleaf forest

### 2019-08-06 manuscript/climate_sensitivity_draft.Rmd
Updated with small changes

```{r, Table 1, eval=TRUE, echo=FALSE, message=FALSE}
library(readxl)
library(kableExtra)
Table1 <- read_xlsx("tables_figures/Table1.xlsx")
Table1 <- sapply(Table1, as.character)
Table1[is.na(Table1)] <- " "

kable(Table1) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```

@@

**Figure 1. Time series of peak growing season (May-August) climate conditions and residual chronologies for each species.** Droughts analyzed here are indicated by dashed lines, and shading indicates the pre-drought period used in calculations of the resistance metric. Figure modified from [@helcoski_growing_2019].
![Time series of combined tree cores by species](tables_figures/Time_series_for_each_species.jpg){width=500px}

@@

```{r, Table 1, eval=TRUE, echo=FALSE, message=FALSE}
traits_test <- read.csv("tables_figures/tested_traits_all.csv")
kable(traits_test, booktabs=TRUE, format = "latex", caption = "All variables tested for climate sensitivity against appropriate null models, in line with hypothesis predictions. Each variable was tested for each drought scenario excepting \"year\" ") %>%
  kableExtra::landscape()
  # kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "scale_down")

>>>>

![Table 1](tables_figures/Table1.png){width=500px}

@@

**Figure 1. Time series of peak growing season (May-August) climate conditions and residual chronologies for each species.** Droughts analyzed here are indicated by dashed lines, and shading indicates the pre-drought period used in calculations of the resistance metric. Figure modified from [@helcoski_growing_2019].

![Time series of combined tree cores by species](tables_figures/Time_series_for_each_species.jpg){width=500px}

@@

```{r, Table x, eval=TRUE, echo=FALSE, message=FALSE}
traits_test <- read.csv("tables_figures/tested_traits_all.csv")
traits_test$null_model <- gsub("resist.value ~ ", "", traits_test$null_model)
traits_test$tested_model <- NULL
traits_test$null_model_year <- gsub("resist.value ~ ", "", traits_test$null_model_year)
traits_test$tested_model_year <- NULL

kable(traits_test, booktabs=TRUE, format = "latex", caption = "All variables tested for climate sensitivity against appropriate null models, in line with hypothesis predictions. Each variable was tested for each drought scenario excepting \"year\" ") %>%
  kableExtra::landscape()
  # kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "scale_down")
